---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# My wordle implementation

This is my implementation of Wordle using R and R Shiny. 

The [7 figures worth](https://www.bbc.co.uk/news/business-60208463) original can be found here: [powerlanguage.co.uk/wordle/](https://www.powerlanguage.co.uk/wordle/). 

I implemented Wordle in R to eventually add Polish version, but also because I wanted to play around with data exploration. Also, I was interesting how good can a simple regexp solver be, and if how, I humble human, fare in comparison with the machine. 

## Dictionaries

As a source of words for my wordle I use the `words::words` data frame. `words` is the package with list of English Words from the Scrabble Dictionary. You can find more details here: [condwanaland/words](https://github.com/condwanaland/words).

## Installation

You can install the package from github. 

```{r eval=FALSE}

if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}

devtools::install_github("kzkedzierska/my_wordle")
```

